Blockchain technologies promise to reduce one of the great annoyances of modern medical practice: ``credentialing''. Hospitals use the credentialing process to make sure that its physicians are competent and trustworthy. In a sense, credentialing is the hospital's way of performing ``due diligence'' on a physician. 

But today this process imposes a huge burden, both on the physician applying for affiliation and the hospital that must vet the applications.

\subsubsection{The physician gathers credentials, many on paper}
Any physician who wishes to become affiliated with a hospital begins the process by gathering
copies of all their professional credentials, such as:

\begin{itemize}
\item Medical school diploma
\item Certificates of any residencies and fellowships completed
\item Certificates from any specialty medical boards 
\item All state medical licenses 
\item Evaluations from peers
\item Proof of meeting requirements for continuing medical education 
\item Letters from hospitals where the physician was previously affiliated, explaining how and why  the affiliation ended 
\item Details of any malpractice suits 
\end{itemize}

Many of these documents were originally provided on paper, so the physician may need to scan in  paper copies, and manage a set of scanned images or PDFs. 

\subsubsection{The hospital checks credentials and calls a meeting}
On the hospital's side, the Credentialing Office checks the physician's documentation for completeness, accuracy, and authenticity. 
This is an exacting task. 
Almost inevitably, they find shortfalls and go back to the doctor for missing documents. 

Then the Credentialing Office verifies some or all of the physician's documentation. 
For example, they may phone a medical school to confirm that the physician did indeed graduate from there. 
This is clearly a time-intensive process.

Once the documentation is determined to be complete, accurate, and authentic, the hospital's
Credentialing Committee---which typically includes physicians and administrators---meets to decide whether the physician can begin practicing in affiliation with the hospital.

The entire credentialing process is paper-bound, time-consuming, and low-trust. And it can take weeks or even months until any physician is cleared to affiliate with a hospital.

\subsubsection{Three key questions for any blockchain solution}
An effective blockchain solution for medical credentialing must answer three key questions about content, identities, and resources.

1. Will actual content or only pointers to content be placed on the blockchain? 
Credentialing solutions might place public information (such as state medical licensing) on the blockchain itself.  
However, private information (such as peer reviews) might be better stored off the chain; this would guard against any loss of keys, and enable users to remove---but not change---private information.  

2. What's the best way to manage the identities of many participants? 
An ambitious credentialing solution might include every hospital, every physician, every source of continuing medical education, and so on. 
This could eventually number thousands of participants. 
How will so many identities be efficiently and securely managed?

3. What resources are required, especially for storage? 
Credentialing solutions may be in service for decades, requiring significant resources for processing, communication, and storage. 
For example, what if at some point credentialing organizations want video testimony from peers? Storage requirements could skyrocket---and who would cover that added cost? 

\subsubsection{Hyperledger can help streamline credentialing}
Credentialing provides a good use case for blockchain technologies, which can simplify and streamline every step of the process. 

\textbf{Hyperledger Indy} provides off-the-shelf solutions that would otherwise require architecting and developing new software. 
One significant feature: Indy implements the proposed W3C standard for verifiable claims, supporting the pairwise exchange of selected credentials. In practice, this can work as follows:
\begin{enumerate}
\item A physician requests proof of graduation from their medical school.
\item The physician places a digital credential on the blockchain, where it's considered irrefutable and tamper-proof.
\item A hospital can access the blockchain to verify the physician's credential, with no need to contact the medical school directly. 
\item The physician can expose only the specific credentials the hospital requires, and nothing more. 
\end{enumerate}

This implementation of verifiable claims safeguards the physician's privacy, saves time and effort for everyone involved, and streamlines the entire process. At last: a better way to handle medical credentialing.
